Data Preparation

### 2019-01-11 Data Preparation.Rmd
data preparation debugged

rm(stems, stem_hunspell)
print(d_overview_stem) # See humanities - humanity
```
### Removing Stopwords
```{r}

@@

d_description <- remove_sw(d_description)
d_overview <- remove_sw(d_overview)
d_manual <- remove_sw(d_manual)
```

@@

```{r}

@@

```
From count_after we see that student 544450 has two passed capstones at different moments in time, we already knew this and we must ask Richard why this is the case. However, since both capstones where passed in 2010, this creates no problem for our current purposes. However, let's remove the later version.
We will also rename `Year` to `Capstone Year` and keep only the columns `Capstone Year` and `ID`
```{r}
to_remove <- capstone_finish_year%>%
  filter(ID==544450)
to_remove <- to_remove[duplicated(to_remove$ID),]

>>>>

rm(stems, stem_hunspell, stem_with_dictionary)
print(d_overview) # See humanities - humanity
```
### Removing Stopwords
```{r}

@@

d_description <- remove_sw(d_description)
d_overview <- remove_sw(d_overview)
d_manual <- remove_sw(d_manual)

rm(sw_own, remove_sw)
```

@@

@@

```
From count_after we see that student 544450 has two passed capstones at different moments in time, we already knew this and we must ask Richard why this is the case. However, since both capstones where passed in 2010, this creates no problem for our current purposes. However, let's remove the later version.
We will also rename `Year` to `Capstone Year` and keep only the columns `Capstone Year` and `ID`
```{r, eval = FALSE}
to_remove <- capstone_finish_year%>%
  filter(ID==544450)
to_remove <- to_remove[duplicated(to_remove$ID),]
